Scalable Clustering of Genotype Information using MapReduce

### 2014-05-16 doc/publications/incob2014/paper.tex
Few changes

\section*{Results and discussion}
\subsection*{Runtime}
Text for this section.

@@

\subsection*{Mahout K-means clustering}
We Cluster samples from a VCF file containing the variants from chromosome one. The content of the VCF file represents

Mahout provides libraries for clustering data, 'sequences', although the data must first be converted from the VCF format to
sequence files. The sequence files should consist of key-value pairs, where
Using a custom Java program, we transpose the

@@

\subsection*{Speed}

>>>>

\section*{Results and discussion}
\subsection*{Runtime}
We measured the runtime seperately for pre-processing stage as well as the k-means clustering stage.

@@

\subsection*{Mahout K-means clustering}
To cluster the samples from the sequence files, we use Mahout 0.9 in conjunction with Hadoop 2.2.0. 
The clustering steps are the same for each sample, however, due to the increased feature size we designate more memory to the
YARN containers. For the first step, we specify \texttt{k}, the number of clusters. The function \texttt{RandomSeedGenerator.buildRandom}
creates a new sequence file containing \texttt{k} random centroids from the samples sequence file. The sequence file
of samples and the sequence file of centroids serve as the input to \texttt{KMeansDriver.run}, a static Mahout API function that launches
a k-means clustering job on the Hadoop service.

@@

\subsection*{Speed}
We measured the speed for various stages of the processing and clustering. We used
